Generating the Blueprints of the Maven Repository

### 2015-01-25 msr.tex
Add ckjm citation

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}\footnote{\url{http://www.spinellis.gr/sw/ckjm/}} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}. The version of the tool that we used for this experinment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.

>>>>

\begin{itemize}
  \item \textbf{CKJM-ext} \textit{(ckjm)}~\cite{Spi05g} is an open source tool that was developed by Diomidis Spinellis and then extended by Marian Jureczko. It calculates many software complexity metrics, including the \textit{Chidamber and Kemmerer} set of metrics \cite{CHKE94}. The version of the tool that we used for this experinment can be found in github\footnote{\url{https://github.com/bkarak/ckjm_ext}}.
